\plaintitle

### 2025-05-21 docs/style/article-body.tex
praying for no merge ocnflicts

Imagine, then, if a malicious attacker somehow manages to ascertain the state a computer was in when it generated a random number, for instance to produce an SSH-key. This attacker then has the opportunity to accurately reproduce the exact, deterministic state that produced said random number, in essence removing the safety that randomness brings. While it may sound unrealistic, the exponential increase in processing power and the burgeoning field of quantum computing does introduce the possibility that one day, what we perceive as random is nothing more than a simple algorithm to crack.

@@

The optical signal output by the device described in \cite{Clason2023} needs to be converted to a stream of random, raw bits via an Analog to Digital Converter (\emph{ADC}). Some post-processing of the said raw bits has to be performed in order to ensure that the bits are workable, and to remove potential deterministic patterns from the data. One method for this post-processing we will explore in this work is Toeplitz extraction \cite{toeplitz}, typically performed on the host computer utilizing the randomly generated numbers. The post-processing finally yields a random number. This relationship can be seen in Figure 1.

@@

\subsubsection{5.1 Implementation strategy}\label{implementation-strategy}

@@

\paragraph{5.2 Phase one}\label{phase-one}

@@

The initial implementation followed the pseudocode described in section 3.4, using matrix multiplication over raw input and seed data. It relied on \texttt{std::vector\textless{}int\textgreater{}} for storage and used nested loops to compute each output bit. From this point, this implementation was improved over the coming iterations, and the new implementation verified in the same manner as the initial version.

@@

\paragraph{5.3 Phase two}\label{phase-two}

@@

\subsubsection{5.4 Evaluation}\label{evaluation}

@@

\subsubsection{5.5 Limitations}\label{limitations}

Our proposed iterations all assume that the limited hardware will support it. Whereas we are confident that Teensy 4.1 will be able to handle each iteration

step (\emph{even the naive implementation}), the remaining microcontrollers with lower specifications might not be suitable for the first iterations. Testing the implementations on different microcontrollers could turn out to be unfeasible -- however, this remains to be seen during the experimentation.

@@

We created a script to facilitate easier testing, which is attached to this paper. Using this script, all bitstrings used for testing can be evaluated against the baseline, ensuring that the output from the new iteration matches the baseline exactly. Furthermore, the script also provides the average execution time of only the Toeplitz extraction in microseconds.

>>>>

Imagine, then, if a malicious attacker somehow manages to ascertain the state a computer was in when it generated a random number, for instance to produce an SSH-key. This hypothetical attacker has the opportunity to accurately reproduce the exact, deterministic state that produced said random number, in essence removing the safety that randomness brings. While it may sound unrealistic, the exponential increase in processing power and the burgeoning field of quantum computing does introduce the possibility that one day, what we perceive as random is nothing more than a simple algorithm to crack.

@@

The optical signal output by the device described in \cite{Clason2023} needs to be converted to a stream of random, raw bits via an Analog to Digital Converter (\emph{ADC}). Some post-processing of the said raw bits has to be performed in order to ensure that the bits are workable, and to remove potential deterministic patterns from the data. One method for this post-processing we will explore in this work is Toeplitz extraction \cite{toeplitz}, typically performed on the host computer utilizing the randomly generated numbers. The post-processing finally yields a random number. This relationship can be seen in Figure \ref{fig:linear-system}.

@@

@@

\subsubsection{5.1 Phase one}\label{phase-one}

@@

The initial implementation followed the pseudocode described in Algorithm \ref{alg:bit-conv}, using matrix multiplication over raw input and seed data. It relied on \texttt{std::vector\textless{}int\textgreater{}} for storage and used nested loops to compute each output bit. From this point, this implementation was improved over the coming iterations, and the new implementation verified in the same manner as the initial version.

@@

\subsubsection{5.2 Phase two}\label{phase-two}

@@

\subsubsection{5.3 Evaluation}\label{evaluation}

@@

\subsubsection{5.4 Limitations}\label{limitations}

Our proposed iterations all assume that the limited hardware will support it. Whereas we are confident that Teensy 4.1 will be able to handle each iteration step (\emph{even the naive implementation}), the remaining microcontrollers with lower specifications might not be suitable for the first iterations. Testing the implementations on different microcontrollers could turn out to be unfeasible -- however, this remains to be seen during the experimentation.

@@

We created a script to facilitate easier testing, which is attached to this paper. Using this script, all bitstrings used for testing can be evaluated against the baseline, ensuring that the output from the new iteration matches the baseline exactly. Furthermore, the script also provides the average execution time of only the Toeplitz extraction in microseconds. A brief overview of the architecture of this test script can be seen in Figure \ref{fig:testscript-architecture}.

\begin{figure*}[ht] \centering
\includegraphics[width=\textwidth]{img/testscript.png} \caption{A brief overview
of the testscript architecture.} \label{fig:testscript-architecture}
\end{figure*}
